Towards something :-D

### 2015-03-25 paper/nodalida2015.tex
change CGSAT to SATCG (it's not a type of SAT, it's a type of CG :-P)
add numbers for p&p and don quijote

We took small constraint grammars (\textless{}500 rules) for Spanish and English, and disambiguated a number of texts from Project Gutenberg. We compared the result of using VISLCG3 for the same task; table~\ref{table:results} shows the differences in results in both sentence and word level.

\begin{table}
  \centering
  \begin{tabular}{|r|r|r|r|r|}
     \hline
    \textbf{Text} & \textbf{Diff words} & \textbf{Diff sentences} \\
    \hline
	Pride and Prejudice & todo & 5k/7k \\  
    \hline
       Don Quijote & todo & 3k/6k  \\ 
     \hline
  \end{tabular}
  \caption{Results for comparing CGSAT and VISLCG3.}
  \label{table:results}
\end{table}

The tendency of needing less rules to disambiguate shows also in a larger context with more complex rules.
In many of the differences, CGSAT disambiguated more. (TODO counts)

>>>>

We took small constraint grammars (\textless{}500 rules) for Spanish and English, and disambiguated a number of texts from Project Gutenberg. Table~\ref{table:results} shows how much the results agree with the result given by VISL CG3 parser with the same grammar and text.

\begin{table}
  \centering
  \begin{tabular}{|l|c|c|}
     \hline
    \textbf{Text} & \textbf{Words} & \textbf{\% same analyses} \\
    \hline
	Pride and Prejudice & 153386 & 90.6 \\  
    \hline
       Don Quijote & 186460 & 96.3  \\ 
     \hline
  \end{tabular}
  \caption{Results for comparing SATCG and VISLCG3.}
  \label{table:results}
\end{table}

The tendency of needing less rules to disambiguate shows also in a larger context with more complex rules.
In many of the differences, SATCG disambiguated more. (TODO counts)
